### 2018-04-10 Paper/bayes.tex
..

\noindent where $\bm{X}$ is the set of uncertain model parameters, and $\bm{Y}$ is the available set of
experimental data i.e. bulk thermal conductivity at different temperatures in the present case. 
We exploit our findings based on sensitivity analysis in
Figure~\ref{fig:gsa} and focus on calibrating $\alpha$ and $\gamma$ i.e. $\bm{X}:\{\alpha,\gamma\}$.
$\mathcal{P}(\bm{X}\vert \bm{Y})$ is regarded as the posterior, $\mathcal{P}(\bm{Y}\vert\bm{X})$ is the
`likelihood', and $\mathcal{P}(\bm{X})$ is the prior probability distribution (referred to as the `prior') of $\bm{X}$.
The likelihood accounts for measurement error, and the discrepancy between experiments and model
predictions, whereas, the prior is an initial guess for the distribution of uncertain model parameters in an
interval. It also accounts for the availability of an expert opinion pertaining to their estimates. 
The posterior provides an estimate of the most likely value of the uncertain model parameters based on
prior uncertainty, experimental data used for calibration and the associated measurement error, and model
discrepancy. Additionally, the posterior is often used to quantify the uncertainty associated with model predictions. Several algorithms based on Markov chain Monte Carlo (MCMC) technique are available for  
sampling the posterior~\cite{Haario:2001, Haario:2006,Xu:2014}.

Evaluating the joint posterior of $\alpha$ and $\gamma$ using MCMC typically requires a large amount of
computational effort and is not the focus on this work. Instead, we compute and plot the joint likelihood on
a 2D cartesian grid described by $\alpha$ and $\gamma$ using Eq.~\ref{eq:like} as illustrated in
Figure~\ref{fig:like}(a). For this purpose, we consider $\alpha$ and $\gamma$ to be
independent and uniformly distributed in the intervals, [1.62,1.98] and [1.08,1.32] respectively. 
Consequently, the joint posterior is proportional to the likelihood, considered to be a Gaussian:

@@

Approximate marginal distributions for
$\alpha$ and $\gamma$ are shown in Figure~\ref{fig:like}(b) and Figure~\ref{fig:like}(c) respectively. 
It must be noted that the joint likelihood plot is essentially for the purpose of illustration. The actual posterior
should be evaluated using a substantially large set of experimental data and surrogates for NEMD predictions
need to be constructed (as discussed in Section~\ref{sec:ros}) for each temperature to reduce computational effort. 
The dimensionality of the surrogate could potentially be reduced a priori using DGSM and a posteriori using
Sobol sensitivity analysis as presented in this work.

>>>>

\noindent where $\bm{X}$ is the set of uncertain model parameters, and $\bm{Y}$ is the available set of
experimental data i.e. bulk thermal conductivity at different temperatures in the present case. 
We exploit our findings based on sensitivity analysis in
Figure~\ref{fig:gsa} and focus on calibrating $\alpha$ and $\gamma$ i.e. $\bm{X}:\{\alpha,\gamma\}$.
$\mathcal{P}(\bm{X}\vert \bm{Y})$ is regarded as the posterior, $\mathcal{P}(\bm{Y}\vert\bm{X})$ is the
`likelihood', and $\mathcal{P}(\bm{X})$ is the joint prior probability distribution (referred to as the `prior') of $\bm{X}$.
The likelihood accounts for measurement error, and the discrepancy between experiments and model
predictions, whereas, the prior is an initial guess for the distribution of uncertain model parameters in an
interval. It also accounts for the availability of an expert opinion pertaining to their estimates. 
The posterior provides an estimate of the most likely value of the uncertain model parameters based on
prior uncertainty, experimental data used for calibration and the associated measurement error, and model
discrepancy. Additionally, the posterior is often used to quantify the uncertainty associated with model predictions. Several algorithms based on Markov chain Monte Carlo (MCMC) technique are available for  
sampling the posterior~\cite{Haario:2001, Haario:2006,Xu:2014}.

Evaluating the joint posterior of $\alpha$ and $\gamma$ using MCMC typically requires a large amount of
computational effort and is not the focus on this work. Instead, we compute and plot the joint likelihood on
a 2D cartesian grid described by $\alpha$ and $\gamma$ using Eq.~\ref{eq:like} as illustrated in
Figure~\ref{fig:like}(a). For this purpose, we consider $\alpha$ and $\gamma$ to be
independent and uniformly distributed in the intervals, [1.62,1.98] and [1.08,1.32] respectively. 
Consequently, the posterior is proportional to the likelihood, considered to be a Gaussian:

@@

Approximate marginal distributions for
$\alpha$ and $\gamma$ are shown in Figure~\ref{fig:like}(b) and Figure~\ref{fig:like}(c) respectively. 
It must be noted that the joint likelihood plot is essentially for the purpose of illustration. The actual posterior
should be evaluated using a substantially large set of experimental data for bulk thermal conductivity as a function
of temperature, and surrogates for NEMD predictions
need to be constructed (as discussed in Section~\ref{sec:ros}) at each temperature for which the data is made
available in order to reduce computational effort. 
The dimensionality of the surrogate could potentially be reduced a priori using DGSM and a posteriori using
Sobol sensitivity analysis as presented in this work.

### 2018-04-10 Paper/disc.tex
..

A possible enhancement of nominal SW parameter estimates for a given application
and the choice of material system is also highlighted in this work. To enable this,
we focus our efforts on understanding the sensitivity of predictions on the 
parameters. For this purpose, we estimate the so-called derivative based sensitivity
measures (DGSM) using random samples in the 7D parameter space. While individual
measures for the 7 parameters are not too distant from each other, the predictions
seem to be most sensitive towards $\gamma$. Sensitivity measures for $\alpha$,
$\lambda$, $q$, and $A$ are found to be comparable while those for $B$ and $p$
are relatively small.

A polynomial chaos surrogate model for the bulk thermal conductivity (observable)
as a function of SW potential
parameters at a given temperature is constructed. The surrogate helps reduce the
computational effort required for forward propagation of the uncertainty from
parameters to the observable as well as for estimating the Sobol sensitivity indices.
Furthermore, the surrogate could be used to accelerate parameter calibration in a
Bayesian setting. However, since the surrogate relies on NEMD predictions, the
underlying computational effort is nevertheless significantly large. To circumvent
this challenge, we exploit our initial findings based on DGSM and construct
a reduced order surrogate in 5 dimensions by fixing the parameters, $B$ and $p$.
We verify its accuracy by estimating the relative
L-2 norm of the error between NEMD predictions in the full space and the reduced
order surrogate predictions, and comparing the probability distribution of the
bulk thermal conductivity in Figure~\ref{fig:verify}. Furthermore, our initial
sensitivity trends based on DGSM-analysis using 25 samples seems to agree favorably
with Sobol sensitivity analysis based on 10$^{6}$ samples. Hence, it can be said
that DGSM-based analysis with a few samples could offer huge computational gains
by reliably reducing the dimensionality of a surrogate for uncertainty analysis.

Finally, we highlight key aspects of parameter calibration in a Bayesian setting.
The underlying motivation stems from the fact that the nominal estimates of the SW
parameters did not consider measurement error, simulation noise, model form error,
and parametric uncertainties. Calibration in a Bayesian framework allows us to
incorporate such errors and uncertainties in an efficient manner and provides
a joint posterior distribution of the uncertain parameters. To minimize computational
costs pertaining to the calibration process, we suggest the following sequence of
steps: First, perform DGSM analysis to 
identify parameter that are not so important. Second, construct a reduced order
surrogate based on DGSM-analysis. Third, verify the accuracy of the surrogate
and compute Sobol indices. Fourth, consider only the important parameters in
calibration and construct a second surrogate in the reduced subspace. Fifth,
quantify the surrogate error to be accounted for during calibration. Sixth,
evaluate the joint posterior using an efficient MCMC-based algorithm.

>>>>

A possible enhancement of nominal SW parameter estimates for a given application
and the choice of material system is also highlighted in this work. To enable this,
we focus our efforts on understanding the sensitivity of predictions on individual potential
parameters. For this purpose, we estimate the so-called derivative based sensitivity
measures (DGSM) using random samples in the 7D parameter space. While individual
measures for the 7 parameters are not too distant from each other, the predictions
seem to be most sensitive towards $\gamma$. Sensitivity measures for $\alpha$,
$\lambda$, $q$, and $A$ are found to be comparable while those for $B$ and $p$
are relatively small.

A polynomial chaos surrogate model for the bulk thermal conductivity (observable)
as a function of SW potential
parameters at the bulk temperature of 300~K is constructed. The surrogate helps reduce the
computational effort required for forward propagation of the uncertainty from
parameters to the observable as well as for estimating the Sobol sensitivity indices.
Furthermore, the surrogate could be used to accelerate parameter calibration in a
Bayesian setting. However, since the surrogate relies on NEMD predictions, the
underlying computational effort is nevertheless significantly large. To circumvent
this challenge, we exploit our initial findings based on DGSM and construct
a reduced order surrogate in 5 dimensions by fixing the parameters, $B$ and $p$.
We verify its accuracy by estimating the relative
L-2 norm of the error between NEMD predictions in the full space and the reduced
order surrogate predictions, and comparing the probability distribution of the
bulk thermal conductivity in Figure~\ref{fig:verify}. Furthermore, our initial
sensitivity trends based on DGSM-analysis using 25 samples seem to agree favorably
with Sobol sensitivity analysis based on 10$^{6}$ samples. Hence, it can be said
that DGSM-based analysis with a few samples could offer huge computational gains
by reliably reducing the dimensionality of a surrogate for uncertainty analysis.

Finally, we highlight key aspects of parameter calibration in a Bayesian setting.
The underlying motivation stems from the fact that the nominal estimates of the SW
parameters did not consider measurement error, simulation noise, model form error,
and parametric uncertainties. Calibration in a Bayesian framework allows us to
incorporate such errors and uncertainties in an efficient manner and provides
a joint posterior distribution of the uncertain parameters. To minimize computational
costs pertaining to the calibration process, we suggest the following sequence of
steps: First, perform DGSM analysis to 
identify parameters that are not so important. Second, construct a reduced order
surrogate based on DGSM-analysis. Third, verify the accuracy of the surrogate
and compute Sobol indices. Fourth, consider only the important parameters in
calibration and construct a second surrogate in the reduced subspace. Fifth,
quantify the surrogate error to be accounted for during calibration. Sixth,
evaluate the joint posterior using an efficient MCMC-based algorithm.

### 2018-04-10 Paper/ros.tex
..

As discussed earlier in Section~\ref{sec:response}, several strategies are available to
estimate the PC coefficients, $c_{\bm{s}}$. However, since the polynomial basis functions
($\Psi_{\bm{s}}(\bm{\xi}$)) are
relatively high dimensional, we use a computationally efficient approach proposed by
Blatman and Sudret to construct a PCE with sparse basis($\mathcal{A}$) using the LAR
algorithm~\cite{Blatman:2011}. Furthermore, since the NEMD simulations are compute-intensive,
estimating the PC coefficients in the 7D parameter space would still require large amount of
computational resources. Hence, we explore the possibility of reducing the dimensionality of
the surrogate. For this purpose, we 
exploit our observations in Figure~\ref{fig:ub} where a significant
jump in $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and thereby construct the 
PC surrogate in a 5D parameter space by fixing $B$ and $p$ at their nominal values. In the above
equation, $\bm{\xi}:~\{\xi_1(A),\xi_2(q),\xi_3(\alpha),\xi_4(\lambda),\xi_5(\gamma)\}$ is a set
of five canonical random variables, $\xi_i$ distributed uniformly in the interval [-1,1].
Prior intervals for the uncertain SW parameters are considered to be
$\pm~10\%$ of their respective nominal estimates except for $q$ in which case it is [0,0.1]. In
Figure~\ref{fig:loo}, we plot the leave-one-out cross-validation error 
($\epsilon_{\tiny{\mbox{LOO}}}$)~\cite{Blatman:2010} as defined
below in Eq.~\ref{eq:loo} against the number of model realizations used to construct the 5D
PC surrogate. UQLab~\cite{Marelli:2014} was used for estimating $\epsilon_{\tiny{\mbox{LOO}}}$ and constructing
the surrogate.

@@

\noindent Since $\epsilon_{\mbox{\tiny{L-2}}}$ is found to be $\mathcal{O}(10^{-2})$, the 5D surrogate can be considered as
reasonably accurate from the perspective of relative L-2 error norm.

In the second strategy, we compare NEMD
predictions and estimates from the 5D surrogate in a probabilistic sense. As shown in Figure~\ref{fig:verify}, a 
histogram plot based on the available set of NEMD predictions in the 7D parameter space is compared with
the bulk thermal conductivity distribution as obtained using the reduced order surrogate and 10$^6$ samples in the
5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$.

@@

It is observed that the probability distribution (PDF) based on estimates from the reduced order surrogate compares
favorably with the histogram plot. Specifically, the corresponding mode values for $\kappa$ from the two plots are
in close agreement, the PDF reasonably captures the peaks observed in the histogram, as well as the spread in
the bulk thermal conductivity distribution. 
Hence, the reduced order surrogate is verified for accuracy in both cases. 
\bigskip

@@

It is found that $\kappa$ is predominantly sensitive towards the choice of $\alpha$ and
$\gamma$. This observation is consistent with our initial findings based on DGSM using 25 samples in the 7D
parameter space. However, the DGSM estimate for $\gamma$ was found to be the highest in that case. 
While sensitivity towards $A$, $q$, and $\lambda$ is observed to be comparatively less in both cases, Sobol
indices for the three parameters are estimated to be smaller by an order of magnitude compared to those
for $\alpha$ and $\gamma$. Large quantitative disagreements in parametric sensitivity between DGSM and the 
Sobol indices is however not unexpected essentially because they differ by construction. The former is based
on an expectation of partial derivatives while the later is based on variance. Nevertheless, significant qualitative
agreements pertaining to parameter importance in the two approaches is quite encouraging. 
Moreover, verification of the reduced order
surrogate for accuracy increases our confidence in implementing DGSM to ascertain relative importance of the
SW potential parameters and hence perform uncertainty analysis for the present application with minimal
computational effort.

>>>>

As discussed earlier in Section~\ref{sec:response}, several strategies are available to
estimate the PC coefficients, $c_{\bm{s}}$. However, since the polynomial basis functions
($\Psi_{\bm{s}}(\bm{\xi}$)) are
relatively high dimensional, we use a computationally efficient approach proposed by
Blatman and Sudret to construct a PCE with sparse basis($\mathcal{A}$) using the LAR
algorithm~\cite{Blatman:2011}. Furthermore, since the NEMD simulations are compute-intensive,
estimating the PC coefficients in the 7D parameter space would still require large amount of
computational resources. Hence, we explore the possibility of reducing the dimensionality of
the surrogate. For this purpose, we 
exploit our observations in Figure~\ref{fig:ub} where a significant
jump in $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and thereby construct the 
PC surrogate in a 5D parameter space by fixing $B$ and $p$ at their nominal values. In the above
equation, $\bm{\xi}:~\{\xi_1(A),\xi_2(q),\xi_3(\alpha),\xi_4(\lambda),\xi_5(\gamma)\}$ is a set
of five canonical random variables, $\xi_i$ distributed uniformly in the interval [-1,1].
Prior intervals for the uncertain SW parameters are considered to be
$\pm~10\%$ of their respective nominal estimates except for $q$ in which case it is [0,0.1]. In
Figure~\ref{fig:loo}, we plot the leave-one-out cross-validation error 
($\epsilon_{\tiny{\mbox{LOO}}}$)~\cite{Blatman:2010}, defined
below in Eq.~\ref{eq:loo}, against the number of model realizations used to construct the 5D
PC surrogate. UQLab~\cite{Marelli:2014} was used for estimating $\epsilon_{\tiny{\mbox{LOO}}}$ and constructing
the surrogate.

@@

\noindent where $\mathcal{M}(\bm{\theta}_{\mbox{\tiny{7D}}}^{(i)})$ is the NEMD prediction in the original 7D
parameter space, and $\mathcal{M}^{PCE}(\bm{\theta}_{\mbox{\tiny{5D}}}^{(i)})$ is the corresponding 
estimate using the reduced order surrogate (5D). 
Since $\epsilon_{\mbox{\tiny{L-2}}}$ is found to be $\mathcal{O}(10^{-2})$, the 5D surrogate can be considered as
reasonably accurate from the perspective of relative L-2 error norm.

@@

In the second strategy, we compare NEMD
predictions and estimates from the 5D surrogate in a probabilistic sense. As shown in Figure~\ref{fig:verify}, a 
histogram plot based on the available set of NEMD predictions for bulk thermal conductivity in the 7D parameter 
space is compared with its probability distribution, obtained using the reduced order surrogate and
10$^6$ samples in the 5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$. It is observed that the probability distribution (PDF) based on estimates from the reduced order surrogate compares
favorably with the histogram. Specifically, the corresponding mode values for $\kappa$ from the two plots are
in close agreement, and the PDF reasonably captures the peaks as well as the spread in
the bulk thermal conductivity distribution as observed in the histogram. 
Hence, the reduced order surrogate is verified for accuracy in both cases. 
\bigskip

@@

It is found that $\kappa$ is predominantly sensitive towards the choice of $\alpha$ and
$\gamma$. This observation is consistent with our initial findings based on DGSM using 25 samples in the 7D
parameter space. However, the DGSM estimate for $\gamma$ was found to be the highest in that case. 
While sensitivity towards $A$, $q$, and $\lambda$ is observed to be comparatively less in both cases, Sobol
indices for the three parameters are estimated to be smaller by an order of magnitude compared to those
for $\alpha$ and $\gamma$. Large quantitative disagreement in parametric sensitivity between DGSM and the 
Sobol indices is however not unexpected essentially because the two metrics differ by construction.
The former is based
on an expectation of partial derivatives while the later is based on variance. Nevertheless, significant qualitative
agreement pertaining to parameter importance in the two approaches is quite encouraging. 
Moreover, verification of the reduced order
surrogate for accuracy increases our confidence in implementing DGSM to ascertain relative importance of the
SW potential parameters and hence perform uncertainty analysis for the present application with minimal
computational effort.
